---
title: "Simple document"
author: Mengfan Luo
date: 2021-9-16
output: 
  html_document:
    toc: True
    toc_float: True
    code_folding: hide
---

Put libraries at the top.

```{r, message=FALSE}
library(tidyverse)
```




I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a *normal distribution*:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3

Write a new code chunk

The code chunk import the 'tidyverse',create a dataframe, and makes a histogram.

inside the chunk name can have options including:
echo=FALSE,collapse=TRUE,message=FALSE


```{r new_code_chunk}
#library(tidyverse)

set.seed(1234)

plot_df = 
  tibble(
    x = rnorm(1000, sd = .5),
    y = 1 + 2 * x + rnorm(1000),
    y_quad = 1 + 2 * x^2 + rnorm(1000)
  )
plot_df



ggplot(plot_df,aes(x = x)) + geom_histogram()


```


# Learning assessment: 

Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE

```{r Learning_assesment}
learning_df = 
  tibble(
    sample = rnorm(500, mean = 1),
    vec_logic = sample > 0,
    abs_val = abs(sample)
  )

ggplot(learning_df,aes(x = abs_val)) + geom_histogram()

```

Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell






















